Scalable Clustering of Genotype Information using MapReduce

### 2014-05-17 doc/publications/incob2014/paper.tex
small change to intro

We therefore link the two areas by providing an interface between Mahout and the standard variant data format, variant call format (VCF)~\cite{1KG2012}, which opens up the application of Mahout's different machine learning algorithms to be applied to genotype-based tasks.   
To demonstrate the capability we cluster variant datasets from the 1000 genomes project to determine population structure as well as ancestry using different algorithms available in Mahout. In the first two sections we benchmark the performance and accuracy of Mahout's implementations against standard R based implementations on a reduced version of the data and in the last section we investigate the performance on the full dataset, demonstrating how seamless Mahout can transit to population-scale tasks.

>>>>

We therefore link the two areas by providing an interface between Mahout and the standard variant data format, variant call format (VCF)~\cite{1KG2012}, which opens up the application of Mahout's different machine learning algorithms to be applied to genotype-based tasks.   
To demonstrate the capability we cluster variant datasets from the 1000 genomes project to determine population structure as well as ancestry using the k-means clustering algorithm available in Mahout. In the first two sections we benchmark the performance and accuracy of Mahout's implementations against standard R based implementations on a reduced version of the data and in the last section we investigate the performance on the full dataset, demonstrating how seamless Mahout can transit to population-scale tasks.
